Template for indicator documentation

### 2023-09-12 functional_plant_indicators_seminat.Rmd
RenderBook12092023

### Ecosystem sub-types
And we can show the resulting scaled values as Violin plots for each indicator and main ecosystem type 
```{r,echo=FALSE,message=FALSE, warning=FALSE}

# making the plot, ANO Light, Moist & pH
ggplot(data=subset(res.seminat.ANO,!is.na(scaled_value) & fp_ind %in% c("Light1","Moist1","pH1",
                                                                        "Light2","Moist2","pH2"))
       , aes(x=factor(hovedtype_rute), y=scaled_value, fill=fp_ind)) + 
  geom_hline(yintercept=0.6, linetype="dashed") + 
  geom_violin(color=NA) +
  #  geom_boxplot(width=0.2, color="grey") +
  geom_point(size=1, shape=16, color="black") +
  facet_wrap(~factor(fp_ind,levels=c("Light1","Moist1","pH1",
                                     "Light2","Moist2","pH2")), ncol = 3) + 
  xlab("Main ecosystem type") + 
  ylab("Scaled indicator value (ANO data)") +
  theme(legend.position="none")

>>>>

### Ecosystem sub-types
And we can show the resulting scaled values as Violin plots for each indicator and main ecosystem type 
```{r,echo=FALSE,message=FALSE, warning=FALSE}
res.seminat.ASO$NiN_grunntype2 <- as.factor(substring(res.seminat.ASO$NiN_grunntype,5))
res.seminat.ASO$NiN_grunntype2 <- factor(res.seminat.ASO$NiN_grunntype2, levels=c("C-1","C-2","C-3","C-4","C-5","C-6",
                                                                                  "C-7","C-8","C-9","C-10","C-13","C-20"))
# making the plot, ANO Light, Moist & pH
ggplot(data=subset(res.seminat.ANO,!is.na(scaled_value) & fp_ind %in% c("Light1","Moist1","pH1",
                                                                        "Light2","Moist2","pH2"))
       , aes(x=factor(hovedtype_rute), y=scaled_value, fill=fp_ind)) + 
  geom_hline(yintercept=0.6, linetype="dashed") + 
  geom_violin(color=NA) +
  #  geom_boxplot(width=0.2, color="grey") +
  geom_point(size=1, shape=16, color="black") +
  facet_wrap(~factor(fp_ind,levels=c("Light1","Moist1","pH1",
                                     "Light2","Moist2","pH2")), ncol = 3) + 
  xlab("Main ecosystem type") + 
  ylab("Scaled indicator value (ANO data)") +
  theme(legend.position="none")
